Toxic Code Snippets on Stack Overflow

### 2017-10-06 cloneoverflow-fse17/rebuttal/rebuttal.txt

We would like to thank the reviewers for their helpful comments. Please find below the answers.

@@

REVIEWER 1

Question 1: 
Previous studies have found serious problems in code copied from Stack Overflow (SO): An et al. [2] found 62 active Android projects to contain 232 exact copies of snippets on SO (confirmed by developers) and 60 apps violate the original license. 126 snippets were found to potentially migrate from one app to another via SO posts (`code laundering’). Acar et al. [1] examined 139 SO threads used by the participants in four Android security-related tasks and found that 83% of them contain insecure snippets. The same security-related problems are discovered in a random sampling of 200,000 apps (e.g. 98.9% implement insecure hostname verifier similarly to the SO examples).

Question 2:
It is known that clone detection tools report a lot of false/trivial clones. We focus on the important ones. The number of 32,533 analysed clone pairs are not trivial clones according to the clone agreement and clone filtering process (making the manual study feasible). However, they are not the 'total' number of clones between SO and Qualitas. Moreover, one can expect a large number of clones to other projects not in Qualitas.

Question 3:
Classifications of clones by humans are known to be very subjective. However, we expect similar results with different evaluators or a higher number of evaluators.

Question 4:
Although the code is provided as minimum working examples, it is known that the code is used as-is and causing problems in active projects [1,2]. Active maintenance and support provided by SO could mitigate such problems.

@@

REVIEWER 2

Question 1:
We are not aware of any curated set of software that includes non-open source projects. We focused on open source projects to allow replication of our study.

Question 2:
See Table 11: 79 (QS) and 77 (EX) pairs (snippets) violate the license but acknowledge the source, 202 (UD) pairs violate licenses and have no acknowledgement.

@@

REVIEWER 3

Question 1:
Disagreed clone pairs are also clones, they just have lower confidence to be true clones. By only inspecting agreed clones, one would miss several true clones due to the tools' differences [61].

Question 3:
We consider them as two clone pairs. In the set of 671 QS+EX+UD clones pairs, a clone in Qualitas is appearing, on average, in 1.2 SO answers.

### 2017-10-06 cloneoverflow-fse17/cloneoverflow_fse17.tex
Renamed old paper to "cloverflow-fse17".

\begin{document}
	\title{Outdated and License-Violating Code on Stack Overflow}
	%\titlenote{Produces the permission block, and
	%  copyright information}
	%\subtitle{Extended Abstract}
	%\subtitlenote{The full version of the author's guide is available as
	%  \texttt{acmart.pdf} document}

@@

\begin{abstract}
  % We studied online code clones on the popular programming Q\&A
  % website, Stack Overflow, and their issues on outdated code and
  % software licensing violations. 
  Online code clones are code fragments that are copied from software
  projects or online sources to Stack Overflow as examples in
  questions and answers.
  % They can be discovered by using code clone
  % detectors, yet they are inherently different from normal code clones
  % in software projects in several aspects. 
  Due to an absence of a checking mechanism after the code has been
  copied to Stack Overflow, online code clones may suffer from
  becoming outdated or violating the original software license.
  % Moreover, we also found that majority of online code clones do not
  % contain the license of their originals.
  We present a study incorporating several state-of-the-art tools and
  techniques to automatically extract, prioritise, and filter detected
  online clone pairs between 144,064 Java code snippets on Stack
  Overflow and 111 Java open source projects in the curated Qualitas
  corpus. We discovered and analysed 32,533 non-trivial online clone
  candidates. Our investigation of 3,636 manually confirmed clone
  pairs revealed strong evidence that 112 clones have been copied from
  a Qualitas project to Stack Overflow.  We found 64 of them (57\%) 
  to be outdated and potentially harmful for reuse.  Furthermore, we
  found 357 code snippets on Stack Overflow that violate the license
  of their original software.
  % These snippets are questionable for reuse.
  % Our study is among the first to address the problem of
  % outdated and license-violating code snippets on Stack Overflow.
\end{abstract}

>>>>

\begin{document}
	\title{Toxic Code Snippets on Stack Overflow}
	%\titlenote{Produces the permission block, and
	%  copyright information}
	%\subtitle{Extended Abstract}
	%\subtitlenote{The full version of the author's guide is available as
	%  \texttt{acmart.pdf} document}

@@

\begin{abstract}
  % We studied online code clones on the popular programming Q\&A
  % website, Stack Overflow, and their issues on outdated code and
  % software licensing violations. 
 \FIXME{Outdated.~Revise this last}~ Online code clones are code fragments that are copied from software
  projects or online sources to Stack Overflow as examples in
  questions and answers.
  % They can be discovered by using code clone
  % detectors, yet they are inherently different from normal code clones
  % in software projects in several aspects. 
  Due to an absence of a checking mechanism after the code has been
  copied to Stack Overflow, online code clones may suffer from
  becoming outdated or violating the original software license.
  % Moreover, we also found that majority of online code clones do not
  % contain the license of their originals.
  We present a study incorporating several state-of-the-art tools and
  techniques to automatically extract, prioritise, and filter detected
  online clone pairs between 144,064 Java code snippets on Stack
  Overflow and 111 Java open source projects in the curated Qualitas
  corpus. We discovered and analysed 32,533 non-trivial online clone
  candidates. Our investigation of 3,636 manually confirmed clone
  pairs revealed strong evidence that 112 clones have been copied from
  a Qualitas project to Stack Overflow.  We found 64 of them (57\%) 
  to be outdated and potentially harmful for reuse.  Furthermore, we
  found 357 code snippets on Stack Overflow that violate the license
  of their original software.
  % These snippets are questionable for reuse.
  % Our study is among the first to address the problem of
  % outdated and license-violating code snippets on Stack Overflow.
\end{abstract}
